Arrival Management with Open Data

### 2023-04-04 paper.tex
clean-up / evening stop

Trajectory-based operations (TBO) are a core element of the ongoing
transformation programmes (e.g.~Europe/SESAR, US/Next Gen,
Japan/CARATS). On the conceptual level TBO describe a move from
clearance-based operations to a highly predictable and negotiated
trajectory execution between airspace users and air traffic control. The
TBO concept entails the successive refinement (i.e.~negotiation) between
the parties starting from an inital planned trajectory through
operations and the actual execution of flight. TBO builds on higher
levels of information exchange between planning and flow management
systems and the airborne and ground systems during flight operations.
Figure~\ref{fig-TBO-concept} shows the overall timeline and evolution of
a trajectory.

@@

>>>>

Trajectory-based operations (TBO) are a core element of the ongoing
transformation programs for air navigation services (e.g.~Europe/SESAR,
US/Next Gen, Japan/CARATS). On the conceptual level TBO describe a move
from clearance-based operations to a highly predictable and negotiated
trajectory execution between airspace users and air traffic control. The
TBO concept entails the successive refinement (i.e.~negotiation) between
the parties starting from an inital planned trajectory through
operations and the actual execution of flight. TBO builds on higher
levels of information exchange between planning and flow management
systems and the airborne and ground systems during flight operations.
Figure~\ref{fig-TBO-concept} shows the overall timeline and evolution of
a trajectory.

@@

For this study we postulate the following goal of trajectory based
arrival management: ``\ldots{} to reduce inefficiencies in the
(extended) arrival phase by establishing an arrival sequence to require
less costly sequencing close to the airport absorbing time/distance in
more fuel efficient altitudes.''
